---
title: "IST687_FinalProject"
author: "Brandon Croarkin"
date: "May 6, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = "C:\\Users\\brcro\\OneDrive\\Documents\\Syracuse\\IST 687 - Applied Data Science\\Project\\")
```

## IST 687 - Final Project: Analysis of Airline Delays

```{r}
library(readr)
library(ggplot2)
```

####Importing the Data and Basic Data Exploration

Link to data: https://www.kaggle.com/giovamata/airlinedelaycauses/data

```{r}
#Importing the data
df <- read_csv("DelayedFlights.csv")
```

```{r}
colnames(df)
```

```{r}
#X1 is just a duplicate column of the index so we can drop that
df$X1 <- NULL
colnames(df)
```

```{r}
head(df)
```

```{r}
summary(df)
```

####Data Cleaning

Want to check for missing values in our most important data points (ArrDelay and DepDelay).
```{r}
sum(is.na(df$ArrDelay))
```

I want to explore these data points with missing data a little more. 
```{r}
head(df[is.na(df$ArrDelay)==TRUE,])
```

This seems like a small enough number of missing values that it is ok to just remove these rows. 
```{r}
df_clean <- df[complete.cases(df$ArrDelay),]
head(df_clean)
```

```{r}
sum(is.na(df$DepDelay))
```

####Type 1 Data Questions

What Airline experiences the most/longest delays?

```{r}
#let's see what airlines we have data on
unique(df_clean$UniqueCarrier)
```

This dataset uses unique carrier codes. A full list of these codes and the airlines affiliated with them can be found here: https://www.census.gov/foreign-trade/reference/codes/aircarrier/acname.txt

```{r}
#want to see how many flights each carrier has
a <- table(df_clean$UniqueCarrier)
b <- as.data.frame(a)
colnames(b)[1] <- "Airline"
colnames(b)[2] <- "Flights"
b$percentTotal <- round(b$Flights/sum(b$Flights),digits=4)*100
b[order(-b$Flights),]
```

We can see that WN (Southwest Airlines Co.) has the most flights (19.5% of tota). In tallying delay frequencies, we should make sure to account for them having more total flights than other airlines. 

First, let's explore the delay data a little quickly before subsetting by airline. 

```{r}
ggplot(df_clean, aes(x=ArrDelay))+geom_histogram(fill="blue",bins=30)
```

Can already quickly see that there are outliers in the data. 

```{r}
ggplot(df_clean)+geom_boxplot(aes(x=factor(0),y=ArrDelay))
```

We can notice that there are a lot of outliers for the delays. Let's begin looking at this by airlines. 

```{r}
ggplot(df_clean, aes(x=UniqueCarrier,y=ArrDelay))+geom_boxplot(aes(color=UniqueCarrier),alpha=.5,method="jitter")
```

```{r}
c <- tapply(df_clean$ArrDelay,df_clean$UniqueCarrier,mean)
avgDelay <- mean(df_clean$ArrDelay)
avgDelayCarrier <- as.data.frame(as.table(c))
colnames(avgDelayCarrier)[1] <- "Airline"
colnames(avgDelayCarrier)[2] <- "avgAirlineDelay"
avgDelayCarrier$overallAvgDelay <- avgDelay
avgDelayCarrier$diffFromAvg <- avgDelayCarrier$avgAirlineDelay - avgDelayCarrier$overallAvgDelay
avgDelayCarrier <- avgDelayCarrier[order(-avgDelayCarrier$avgAirlineDelay),]
rownames(avgDelayCarrier) <- NULL
avgDelayCarrier
```

From this, it appears that YV (Mesa Airlines, Inc.) has the longest avgDelay at 55.29 minutes. The airline with the longest delays was AQ (not found) that had the shortest delays at 21.26 minutes. 

```{r}
ggplot(avgDelayCarrier,aes(x=Airline,y=diffFromAvg)) + geom_bar(aes(fill=diffFromAvg),color="black",stat="identity") + scale_fill_gradient2(low = "blue",high="red")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

























































































