---
title: "IST687_FinalProject"
author: "Brandon Croarkin"
date: "May 6, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## IST 687 - Final Project
### Analysis of Airline Delays

The U.S. Department of Transportation's (DOT) Bureau of Transportation Statistics (BTS) tracks the on-time performance of domestic flights operated by large air carriers. Summary information on the number of on-time, delayed, canceled and diverted flights appears in DOT's monthly Air Travel Consumer Report, published about 30 days after the month's end, as well as in summary tables posted on this website. BTS began collecting details on the causes of flight delays in June 2003. Summary statistics and raw data are made available to the public at the time the Air Travel Consumer Report is released.

This version of the dataset was compiled from the Statistical Computing Statistical Graphics 2009 Data Expo and is also available here.

####Importing the Data and Basic Data Exploration

```{r}
#Importing the data
df <- read.csv("~/Syracuse/IST 687 - Applied Data Science/Project/Project Data/DelayedFlights.csv")
```

```{r}
summary(df)
```

```{r}
colnames(df)
```

```{r}
head(df)
```

```{r}
str(df)
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

























































































